<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{cowsay tutorial}
%\VignetteEncoding{UTF-8}
-->

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE
)
```

cowsay tutorial
===============

`cowsay` makes it easy to print messages, warnings, or character strings with various animals and other creatures.

## Installation

Stable version from CRAN

```{r eval=FALSE}
install.packages("cowsay")
```

or dev version from GitHub

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("sckott/cowsay")
```

```{r}
library("cowsay")
```

## The animals

The animals, and other ascii creatures, are all in a single named character vector that is exported from the package. Thus, you can access each animal yourself, and do whatever you want with it. 

As of this writing, there are `r length(animals)` animals.

The names of the animals:

```{r}
sort(names(animals))
```

For example, access the cow

```{r}
cow <- animals[['cow']]
cat(cow)
```

## Say something

We expose the function `say()` in this package, which you can use to envoke any animal in the package, and make it say whatever you want. Some examples:

```{r}
say("why did the chicken cross the road", "chicken")
```

```{r}
say("boo!", "ghost")
```

```{r}
say("nope, don't do that", type = "warning")
```

There's the special `time`, that will print out the time

```{r}
say('time')
```

## It's how you say it

You can use `say()` and give back a string, message, or warning

Message

```{r}
say("hello world", by = "cow")
```

Warning

```{r}
say("hello world", by = "cow", type = "warning")
```

String

```{r}
say("hello world", by = "cow", type = "string")
```
